Run-Time Monitoring with Adjustable Overheads \\Using Dataflow-Guided Filtering

### 2014-09-12 dropping.tex
Various edits.

Here, we have shown the dynamic sequence of operations of the monitor.
The actual static code consists of a set of instructions to be run for each
monitored instruction type. Register and memory addresses are read from
information sent by the main core.

>>>>

Note that this monitoring is performed automatically and transparently with
almost no modification needed to the main program. The only modifications to
the main program that are needed are to initially set metadata, such as setting
the base and bounds addresses on a {\tt malloc} call for array bounds check.
Otherwise, on the commit
of instruction types relevant to the specific monitor, the needed address and
register information is forwarded to the monitor automatically.
Here, we have shown the dynamic sequence of operations executed by the monitor but
the actual static code consists of a set of instructions to be run for each
possible instruction type (load, store, etc.).

### 2014-09-12 evaluation.tex
Edits based on Ji's comments.
Various edits.

We tested our system using benchmarks from SPECint
CPU2006 \cite{spec2006}. Since our implementation of BC depends on the
modification of {\tt malloc} to set array bounds information, we focus on the C
SPECint benchmarks. Although we do not
show results for the C++ benchmarks, we note that the results for UMC, DIFT, and IMP
for these benchmarks are similar to the other results shown. For each
benchmark, we simulated for 2 billion instructions. 
% An initial slack of 2
% million cycles, which is less than 1\% of
% the total execution time, is given for a 1.1x target overhead. This initial
% slack is scaled proportionally for other overhead targets. 
Since LS race detection requires multi-threaded programs, we tested LS using
the SPLASH-2 benchmark set \cite{splash-isca95}. We ran these benchmarks for
200 million instructions.
Unless otherwise specified, an unrestricted, slack-based dropping policy is
used.

@@

% Figure~\ref{fig:evaluation.full_mon} shows the execution times of
% performing full monitoring normalized to the execution times of the benchmarks
% without monitoring. In these results, no filtering or partial monitoring is
% done. 
Our initial results for performing full core-based monitoring show severalfold slowdowns.
UMC shows normalized execution times from 5x to 16x with an average
of 10x. BC shows normalized execution times of 8-24x with an average of
16x while DIFT shows normalized execution times of 4x-14x with an average of
9x. IMP shows normalized execution times from 2-6x with an average of 4x and LS
shows slowdowns of 1.8-3.3x with an average of 2.4x.

% Filter monitoring overheads
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.5in 0 0]{figs/data_filtering.pdf}
    \vspace{-0.2in}
    \caption{Monitoring overheads with filtering null metadata.}
    \label{fig:evaluation.filtering}
    \vspace{-0.1in}
  \end{center}
\end{figure}

Figure~\ref{fig:evaluation.filtering} shows the
normalized execution times with filtering enabled. We see significant
reductions in overhead for all three monitoring schemes. UMC sees normalized
execution times of 1.7-7x with an average of 4x with null metadata filtering.
For BC, normalized execution
times drop from 16x down to 3x on average. The range of normalized execution
times for filtered BC is 1.1-8.3x. 
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
Finally, DIFT sees the largest reduction in overheads with only 10\% overheads
on average after filtering, with a
maximum overhead of 31\% after filtering. This is due, in part, to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would expect to see less filtering. IMP does not have
null metadata and thus is not affected by null metadata filtering.
Overheads for LS (not shown) are 1.03-1.72x after null metadata filtering and the average
overhead observed is 1.33x for the SPLASH-2 benchmarks.
These overheads are similar to previous results for multi-core monitoring with
minimal hardware costs such as LBA \cite{lba-asid06} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

In this section, we evaluate the effectiveness of
using partial monitoring (in addition to filtering) to trade-off coverage for further reduced overheads.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. 
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.

@@

@@

One possible application of partial monitoring with low overheads is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check running for
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored. Each run
was simulated for 200 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that it is likely that at least one
monitoring event in a chain will be dropped with the unrestricted dropping
policy. 
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 5\% increase in coverage with only seven runs.
Over hundreds or thousands of runs, source-only dropping should be able to
reach 100\% code coverage.

>>>>

We tested our system using benchmarks from SPECint
CPU2006 \cite{spec2006}. Since our implementation of BC depends on the
modification of {\tt malloc} to set array bounds information, we focus on the C
SPECint benchmarks. Although we do not
show results for the C++ benchmarks, we note that the results for UMC, DIFT, and IMP
for these benchmarks are similar to the other results shown. For each
benchmark, we simulated for 2 billion instructions. 
% An initial slack of 2
% million cycles, which is less than 1\% of
% the total execution time, is given for a 1.1x target overhead. This initial
% slack is scaled proportionally for other overhead targets. 
Since LS race detection requires multi-threaded programs, we tested LS using
the SPLASH-2 benchmark set \cite{splash-isca95}. We ran these benchmarks for
200 million instructions.

@@

% Figure~\ref{fig:evaluation.full_mon} shows the execution times of
% performing full monitoring normalized to the execution times of the benchmarks
% without monitoring. In these results, no filtering or partial monitoring is
% done. 
% Our initial results for performing full core-based monitoring show severalfold slowdowns.
% UMC shows normalized execution times from 5x to 16x with an average
% of 10x. BC shows normalized execution times of 8-24x with an average of
% 16x while DIFT shows normalized execution times of 4x-14x with an average of
% 9x. IMP shows normalized execution times from 2-6x with an average of 4x and LS
% shows slowdowns of 1.8-3.3x with an average of 2.4x.

% Filter monitoring overheads
\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth, clip=true, trim=0 0.5in 0 0]{figs/data_filtering.pdf}
    \vspace{-0.2in}
    \caption{Monitoring overheads with null metadata filtering.}
    \label{fig:evaluation.filtering}
    \vspace{-0.1in}
  \end{center}
\end{figure}

Figure~\ref{fig:evaluation.filtering} shows the
execution times of performing monitoring with null filtering enabled normalized
to the execution time of the benchmarks without monitoring. UMC sees normalized
execution times of 1.7-7x with an average of 4x.
For BC, normalized execution
are 3x on average and range from 1.1x to 8.3x.
% This is not surprising since in the baseline
% implementation all loads and stores needed to be monitored. However, with
% filtering, only loads and stores corresponding to arrays need to be forwarded.
DIFT sees an average of 10\% overhead with a maximum overhead of 31\% with null
metadata filtering. This is due, in part, to the fact
that for our implementation of DIFT on SPEC
benchmarks, we only mark data read from files as tainted. For most of these
benchmarks, this propagates to relatively few instructions. Instead, if we
targeted network or streaming applications, which have larger amounts of
untrusted input data, we would higher overheads. IMP shows normalized
executions from 2-6x with an average of 4x. Overheads for LS (not pictured) are
1.03-1.72x after null metadata filtering and the average
overhead observed is 1.33x for the SPLASH-2 benchmarks.
These overheads are similar to the overheads seen by previous multi-core
monitoring systems such as LBA-accelerated \cite{lba-isca08} and FADE
\cite{fade-hpca14} (see
Table~\ref{tab:monitoring.previous_overheads}). In
Section~\ref{sec:evaluation.fpga}, we evaluate a higher performance, FPGA-based
monitor that shows low tens of percent of overhead.

@@

In this section, we evaluate the effectiveness of
using partial monitoring to trade-off coverage for reduced overheads.
For these results, we use a slack-based, unrestricted dropping policy.
Figure~\ref{fig:evaluation.bc_sweep} shows the monitoring coverage achieved by
array bounds check as we vary the overhead budget. 
We define \emph{monitoring coverage} as the 
percentage of dynamic checks that are performed 
(indirect jumps in DIFT, loads in UMC, and memory accesses in BC). 
The metric is chosen to understand
how likely an error/attack instance is to be detected on an individual system, 
assuming that errors/attacks are uniformly distributed across checks. 
%While we could not evaluate real errors/attacks due to difficulty in setting up
%a large number of bugs and exploits, we believe that the percentage of checks
%provides a good estimate of detection probability when errors/attacks are 
%uniformly distributed across checks.
Note that this metric is different from the
percentage of monitoring events that are not dropped, which includes
non-check instructions.

@@

From these results, we see that for monitors which many short, independent
chains, such as UMC, source-only dropping can provide better coverage than
unrestricted dropping with the same overhead. For other monitors, such as BC,
source-only dropping is prone to overshoot the overhead target.
Thus, for applications where staying with an overhead target is especially
important, such as soft real-time systems, a slack-based, unrestricted dropping
policy is more appropriate. On the other hand, if occasional slowdowns are
acceptable, then source-only dropping can provide better coverage on average.

@@

One possible application of partial monitoring with low overheads is to enable
cooperative debugging. 
The idea with cooperative debugging is to use partial
monitoring with very low overheads across a large number of users or runs. By
varying the pattern of partial monitoring done on each run, the goal is to
achieve high coverage across multiple runs. Varying the monitoring that is
done for different runs can be achieved by using a probabilistic dropping policy.
Figure~\ref{fig:evaluation.multirun} shows the total
coverage achieved over multiple runs for array bounds check running for
unrestricted and source-only dropping policies with probabilistic dropping.
These numbers are averaged across all benchmarks. Here, we use a 10\%
probability
that events are not dropped. Since the goal is code coverage, coverage here is
measured as the percentage of static instructions which are monitored in at
least one of the runs. Each run
was simulated for 200 million instructions. 
We see that for the unrestricted dropping policy there is almost no increase in
coverage.  This is due to the fact that it is likely that at least one
monitoring event in a chain will be dropped with the unrestricted dropping
policy. 
Instead, source-only
dropping is much better suited for achieving high coverage over multiple runs.
Source-only dropping shows a 5\% increase in coverage with only seven runs.
Over hundreds or thousands of runs, source-only dropping should be able to
reach 100\% code coverage.

### 2014-09-12 introduction.tex
Edits based on Ji's comments.
Various edits.

% Adjustable overhead
Partial monitoring with adjustable overheads is achieved by dynamically
dropping monitoring operations when overheads exceed a specified overhead
budget.  In order to prevent dropped monitoring operations from leading to a
false positive, we need to track these dropped flows.  We present a
hardware-based dataflow tracking engine that keeps track of these dropped
flows. With this architecture, we investigate different policies for deciding
which events to drop for partial monitoring. These different policies show a
trade-off between closely matching the overhead budget and the monitoring
coverage achieved.

>>>>

% Adjustable overhead
Partial monitoring with adjustable overheads is achieved by dynamically
dropping monitoring operations when overheads exceed a specified overhead
budget. Although this results in reduced monitoring coverage (i.e., false
negatives), false positives can also occur due to out-of-date metadata information.
In order to prevent these
false positive, we need to track the dropped metadata flows.  We present a
hardware-based dataflow tracking engine that keeps track of these dropped
flows. With this architecture, we investigate different policies for deciding
which events to drop for partial monitoring. These different policies show a
trade-off between closely matching the overhead budget and the monitoring
coverage achieved.
